Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-25 chap-intro.tex
Mention Tillmann as well
Remove equation reference in parentheses

%KO: commented this out. I think the purity is not important enough
%to deserve another sentence here, since we only vaguely hint
%at "further research".
% KO: Let's have one bullet point per section. Also, a conjecture
% sounds like a rather weak contribution
%\item We argue that incrementalization is efficient on
%  \emph{self-maintainable programs}, and discuss how further research on
%  static or dynamic memoization can speed up a larger class of programs (\cref{sec:performance-cons}).
%  \pg{This contribution references text which is now commented
%    out. I believe the text should be brought back in.}
%
\item We prove that our incrementalizing transformation $\DERIVE$
is correct~(\cref{eq:correctness}) by a novel machine-checked logical relation
proof, mechanized in Agda~\citep{agda-head}.

@@

The first chapters of \cref{part:incr} are originally based on work by \citet*{CaiEtAl2014ILC}, though
significantly revised; only \cref{sec:applying,sec:rw} survive mostly unchanged.
This work was even more of a team effort. I initiated and led the
overall project and came up with the original notion of change structures; Cai
Yufei contributed differentiation itself and its first correctness proof.
\Cref{part:incr} contains novel correctness proof; its history and
contributions are discussed in \cref{sec:ilc-dev-history}.

>>>>

%KO: commented this out. I think the purity is not important enough
%to deserve another sentence here, since we only vaguely hint
%at "further research".
% KO: Let's have one bullet point per section. Also, a conjecture
% sounds like a rather weak contribution
%\item We argue that incrementalization is efficient on
%  \emph{self-maintainable programs}, and discuss how further research on
%  static or dynamic memoization can speed up a larger class of programs (\cref{sec:performance-cons}).
%  \pg{This contribution references text which is now commented
%    out. I believe the text should be brought back in.}
%
\item We prove that our incrementalizing transformation $\DERIVE$
is correct by a novel machine-checked logical relation
proof, mechanized in Agda.

@@

The first chapters of \cref{part:incr} are originally based on work by \citet*{CaiEtAl2014ILC}, though
significantly revised; only \cref{sec:applying,sec:rw} survive mostly unchanged.
This work was even more of a team effort. I initiated and led the
overall project and came up with the original notion of change structures; Cai
Yufei contributed differentiation itself and its first correctness proof.
Tillmann Rendel contributed significant simplifications and started the overall
mechanization effort.
\Cref{part:incr} contains novel correctness proof; its history and
contributions are discussed in \cref{sec:ilc-dev-history}.
